A pipeline to analyse time-course gene expression data

### 2020-06-24 manuscript.tex
Deploy NelleV/2019timecourse-rnaseq-pipeline to github.com/NelleV/2019timecourse-rnaseq-pipeline.git:gh-pages

The manuscript was last compile on 2020-06-17 08:56:13.

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# From CRAN}
\KeywordTok{library}\NormalTok{(NMF)}
\KeywordTok{library}\NormalTok{(ggfortify)}

@@

\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r}
\hline
  & B1 & B2 & B3 & B4 & B5 & B6 & B7 & B8 & B9 & B10 & B11 & B12 & B13 & B14 & B15 & B16 & B17 & B18 & B19 & B20\\
\hline
A\_51\_P114236 & 4 & 2 & 1 & 2 & 1 & 3 & 3 & 2 & 5 & 5 & 2 & 1 & 4 & 1 & 1 & 2 & 5 & 1 & 2 & 1\\
\hline
A\_51\_P172409 & 1 & 5 & 5 & 5 & 5 & 5 & 1 & 3 & 2 & 1 & 3 & 4 & 3 & 3 & 5 & 4 & 2 & 4 & 1 & 4\\
\hline
A\_51\_P188401 & 1 & 5 & 5 & 4 & 5 & 5 & 5 & 3 & 2 & 4 & 4 & 4 & 2 & 3 & 5 & 4 & 2 & 4 & 3 & 4\\
\hline
A\_51\_P191274 & 4 & 2 & 1 & 2 & 1 & 3 & 3 & 2 & 5 & 5 & 2 & 1 & 4 & 1 & 1 & 2 & 5 & 1 & 2 & 1\\
\hline
A\_51\_P226791 & 1 & 4 & 2 & 4 & 3 & 4 & 2 & 1 & 3 & 3 & 4 & 2 & 5 & 2 & 3 & 5 & 2 & 2 & 5 & 3\\
\hline
A\_51\_P277048 & 1 & 1 & 4 & 5 & 5 & 2 & 5 & 5 & 2 & 4 & 3 & 4 & 2 & 5 & 4 & 3 & 4 & 4 & 3 & 5\\
\hline
\end{tabular}

@@

\begin{verbatim}
## R version 3.6.0 (2019-04-26)
## Platform: x86_64-pc-linux-gnu (64-bit)
## Running under: Ubuntu 19.04
## 
## Matrix products: default
## BLAS:   /usr/lib/x86_64-linux-gnu/blas/libblas.so.3.8.0
## LAPACK: /usr/lib/x86_64-linux-gnu/lapack/liblapack.so.3.8.0
## 
## locale:
## [1] C
## 
## attached base packages:
##  [1] stats4    parallel  splines   stats     graphics  grDevices utils    
##  [8] datasets  methods   base     
## 
## other attached packages:
##  [1] RColorBrewer_1.1-2      moanin_0.0.0           
##  [3] BiocWorkflowTools_1.6.2 ggfortify_0.4.6        
##  [5] topGO_2.32.0            SparseM_1.77           
##  [7] GO.db_3.6.0             AnnotationDbi_1.42.1   
##  [9] IRanges_2.14.12         S4Vectors_0.18.3       
## [11] graph_1.58.2            viridis_0.5.1          
## [13] viridisLite_0.3.0       KEGGprofile_1.22.0     
## [15] RCurl_1.95-4.12         bitops_1.0-6           
## [17] NMF_0.21.0              Biobase_2.40.0         
## [19] BiocGenerics_0.26.0     cluster_2.0.9          
## [21] rngtools_1.3.1.1        pkgmaker_0.27          
## [23] registry_0.5-1          ggplot2_3.1.1          
## [25] kableExtra_1.1.0        biomaRt_2.36.1         
## [27] BiocStyle_2.8.2         knitr_1.22             
## [29] limma_3.36.5            usethis_1.5.0          
## [31] devtools_2.0.2          rmarkdown_1.12         
## 
## loaded via a namespace (and not attached):
##  [1] colorspace_1.4-1   rprojroot_1.3-2    XVector_0.20.0    
##  [4] fs_1.3.1           rstudioapi_0.10    remotes_2.0.4     
##  [7] bit64_0.9-7        ClusterR_1.1.9     KEGG.db_3.2.3     
## [10] xml2_1.2.0         codetools_0.2-16   doParallel_1.0.14 
## [13] pkgload_1.0.2      ade4_1.7-13        gridBase_0.4-7    
## [16] png_0.1-7          FD_1.0-12          readr_1.3.1       
## [19] compiler_3.6.0     httr_1.4.0         backports_1.1.4   
## [22] Matrix_1.2-17      assertthat_0.2.1   lazyeval_0.2.2    
## [25] cli_1.1.0          htmltools_0.3.6    prettyunits_1.0.2 
## [28] tools_3.6.0        gmp_0.5-13.5       gtable_0.3.0      
## [31] glue_1.3.1         reshape2_1.4.3     dplyr_0.8.0.1     
## [34] Rcpp_1.0.1         Biostrings_2.48.0  NMI_2.0           
## [37] ape_5.3            nlme_3.1-139       iterators_1.0.10  
## [40] xfun_0.6           stringr_1.4.0      ps_1.3.0          
## [43] testthat_2.1.1     rvest_0.3.3        gtools_3.8.1      
## [46] XML_3.98-1.19      zlibbioc_1.26.0    MASS_7.3-51.4     
## [49] scales_1.0.0       hms_0.4.2          curl_3.3          
## [52] yaml_2.2.0         memoise_1.1.0      gridExtra_2.3     
## [55] TeachingDemos_2.10 stringi_1.4.3      RSQLite_2.1.1     
## [58] desc_1.2.0         foreach_1.4.4      permute_0.9-5     
## [61] pkgbuild_1.0.3     bibtex_0.4.2       geometry_0.4.1    
## [64] rlang_0.4.6        pkgconfig_2.0.2    matrixStats_0.54.0
## [67] evaluate_0.13      lattice_0.20-38    purrr_0.3.2       
## [70] bit_1.1-14         processx_3.3.1     tidyselect_0.2.5  
## [73] plyr_1.8.4         magrittr_1.5       bookdown_0.9      
## [76] R6_2.4.0           DBI_1.0.0          mgcv_1.8-28       
## [79] pillar_1.3.1       withr_2.1.2        abind_1.4-5       
## [82] KEGGREST_1.20.2    tibble_2.1.1       crayon_1.3.4      
## [85] progress_1.2.0     grid_3.6.0         blob_1.1.1        
## [88] callr_3.2.0        git2r_0.25.2       vegan_2.5-4       
## [91] digest_0.6.18      webshot_0.5.1      xtable_1.8-4      
## [94] tidyr_0.8.3        munsell_0.5.0      magic_1.5-9       
## [97] sessioninfo_1.1.1
\end{verbatim}

>>>>

The manuscript was last compile on 2020-06-24 08:14:28.

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# From github}
\KeywordTok{library}\NormalTok{(timecoursedata)}

\CommentTok{# From CRAN}
\KeywordTok{library}\NormalTok{(NMF)}
\KeywordTok{library}\NormalTok{(ggfortify)}

@@

\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r}
\hline
  & B1 & B2 & B3 & B4 & B5 & B6 & B7 & B8 & B9 & B10 & B11 & B12 & B13 & B14 & B15 & B16 & B17 & B18 & B19 & B20 & B21 & B22 & B23 & B24 & B25\\
\hline
AA204140 & 5 & 5 & 5 & 5 & 5 & 1 & 3 & 2 & 1 & 3 & 1 & 3 & 3 & 1 & 5 & 1 & 1 & 4 & 3 & 5 & 4 & 2 & 4 & 1 & 4\\
\hline
AB008911 & 5 & 5 & 1 & 4 & 1 & 2 & 3 & 3 & 2 & 3 & 3 & 3 & 5 & 1 & 5 & 1 & 3 & 4 & 4 & 5 & 5 & 2 & 4 & 1 & 4\\
\hline
AB010313 & 3 & 3 & 1 & 4 & 1 & 2 & 4 & 3 & 2 & 5 & 3 & 1 & 5 & 3 & 3 & 2 & 3 & 5 & 4 & 2 & 5 & 3 & 3 & 4 & 2\\
\hline
AB010342 & 5 & 3 & 1 & 5 & 1 & 1 & 3 & 3 & 1 & 3 & 3 & 3 & 5 & 1 & 5 & 1 & 1 & 4 & 3 & 5 & 4 & 2 & 3 & 4 & 4\\
\hline
AB011473 & 2 & 1 & 2 & 1 & 3 & 3 & 2 & 5 & 5 & 2 & 4 & 4 & 2 & 5 & 2 & 5 & 5 & 1 & 1 & 1 & 2 & 5 & 1 & 2 & 1\\
\hline
AB099518 & 2 & 1 & 2 & 1 & 3 & 3 & 2 & 5 & 5 & 2 & 4 & 4 & 2 & 5 & 2 & 5 & 5 & 1 & 1 & 1 & 2 & 5 & 1 & 2 & 1\\
\hline
\end{tabular}

@@

\begin{verbatim}
## R version 3.6.0 (2019-04-26)
## Platform: x86_64-pc-linux-gnu (64-bit)
## Running under: Ubuntu 19.04
## 
## Matrix products: default
## BLAS:   /usr/lib/x86_64-linux-gnu/blas/libblas.so.3.8.0
## LAPACK: /usr/lib/x86_64-linux-gnu/lapack/liblapack.so.3.8.0
## 
## locale:
## [1] C
## 
## attached base packages:
##  [1] stats4    parallel  splines   stats     graphics  grDevices utils    
##  [8] datasets  methods   base     
## 
## other attached packages:
##  [1] RColorBrewer_1.1-2      moanin_0.0.0           
##  [3] BiocWorkflowTools_1.6.2 ggfortify_0.4.6        
##  [5] timecoursedata_0.0.0    topGO_2.32.0           
##  [7] SparseM_1.77            GO.db_3.6.0            
##  [9] AnnotationDbi_1.42.1    IRanges_2.14.12        
## [11] S4Vectors_0.18.3        graph_1.58.2           
## [13] viridis_0.5.1           viridisLite_0.3.0      
## [15] KEGGprofile_1.22.0      RCurl_1.95-4.12        
## [17] bitops_1.0-6            NMF_0.21.0             
## [19] Biobase_2.40.0          BiocGenerics_0.26.0    
## [21] cluster_2.0.9           rngtools_1.3.1.1       
## [23] pkgmaker_0.27           registry_0.5-1         
## [25] ggplot2_3.1.1           kableExtra_1.1.0       
## [27] biomaRt_2.36.1          BiocStyle_2.8.2        
## [29] knitr_1.22              limma_3.36.5           
## [31] usethis_1.5.0           devtools_2.0.2         
## [33] rmarkdown_1.12         
## 
## loaded via a namespace (and not attached):
##  [1] colorspace_1.4-1   rprojroot_1.3-2    XVector_0.20.0    
##  [4] fs_1.3.1           rstudioapi_0.10    remotes_2.0.4     
##  [7] bit64_0.9-7        ClusterR_1.1.9     KEGG.db_3.2.3     
## [10] xml2_1.3.2         codetools_0.2-16   doParallel_1.0.14 
## [13] pkgload_1.0.2      ade4_1.7-13        gridBase_0.4-7    
## [16] png_0.1-7          FD_1.0-12          readr_1.3.1       
## [19] compiler_3.6.0     httr_1.4.0         backports_1.1.4   
## [22] Matrix_1.2-17      assertthat_0.2.1   lazyeval_0.2.2    
## [25] cli_1.1.0          htmltools_0.3.6    prettyunits_1.0.2 
## [28] tools_3.6.0        gmp_0.5-13.5       gtable_0.3.0      
## [31] glue_1.3.1         reshape2_1.4.3     dplyr_0.8.0.1     
## [34] Rcpp_1.0.1         Biostrings_2.48.0  NMI_2.0           
## [37] ape_5.3            nlme_3.1-139       iterators_1.0.10  
## [40] xfun_0.6           stringr_1.4.0      ps_1.3.0          
## [43] testthat_2.1.1     rvest_0.3.3        gtools_3.8.1      
## [46] XML_3.98-1.19      zlibbioc_1.26.0    MASS_7.3-51.4     
## [49] scales_1.0.0       hms_0.4.2          curl_3.3          
## [52] yaml_2.2.0         memoise_1.1.0      gridExtra_2.3     
## [55] TeachingDemos_2.10 stringi_1.4.3      RSQLite_2.1.1     
## [58] desc_1.2.0         foreach_1.4.4      permute_0.9-5     
## [61] pkgbuild_1.0.3     bibtex_0.4.2       geometry_0.4.1    
## [64] rlang_0.4.6        pkgconfig_2.0.2    matrixStats_0.54.0
## [67] evaluate_0.13      lattice_0.20-38    purrr_0.3.2       
## [70] bit_1.1-14         processx_3.3.1     tidyselect_0.2.5  
## [73] plyr_1.8.4         magrittr_1.5       bookdown_0.9      
## [76] R6_2.4.0           DBI_1.0.0          mgcv_1.8-28       
## [79] pillar_1.3.1       withr_2.1.2        abind_1.4-5       
## [82] KEGGREST_1.20.2    tibble_2.1.1       crayon_1.3.4      
## [85] progress_1.2.0     grid_3.6.0         vegan_2.5-4       
## [88] blob_1.1.1         callr_3.2.0        git2r_0.25.2      
## [91] digest_0.6.18      webshot_0.5.1      xtable_1.8-4      
## [94] tidyr_0.8.3        munsell_0.5.0      magic_1.5-9       
## [97] sessioninfo_1.1.1
\end{verbatim}
